A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-05-03 07-artifact.tex
Finishes refactoring Sections 3 and 6
Improve Artifact Evaluation based on the reviews.

\section{Artifact appendix}

@@

The compiler/distribution of \CEU is available on GitHub:
\url{https://github.com/fsantanna/ceu}

@@

\begin{verbatim}
$ cd tst/
$ ./run.lua
<...> # output with the test programs
stats = {
    count  = 3483,
    trails = 9094,
    bytes  = 52555128,
    bcasts = 0,
    visits = 4065937,
}
\end{verbatim}

@@

@@

>>>>

\section{Artifact Appendix}

@@

The compiler/distribution of \CEU is available on GitHub:

\url{https://github.com/fsantanna/ceu}

The website of \CEU includes an introductory video and an online tutorial:

\url{http://www.ceu-lang.org/}

The language also provides extensive documentation online:

\url{http://fsantanna.github.io/ceu/out/manual/v0.30/}

@@

\begin{verbatim}
$ cd tst/
$ ./run.lua
<...> # output with the test programs
stats = {
    count = 3478,
    trails = 9082,
    bytes = 50803896,
    bcasts = 0,
    visits = 5189770,
}
\end{verbatim}

@@

\subsubsection{Test Cases}

@@

\subsubsection{Sample Programs}

The distribution of \CEU comes with sample programs that can be executed as
follows:

\begin{verbatim}
$ cd /<...>/ceu/               # change to the Céu repository
$ make samples                  # execute all samples one by one
\end{verbatim}

\subsubsection{Single File}

It is also possible to compile a single file with a program in \CEU:

\begin{verbatim}
$ cd /<...>/ceu/                         # change to the Céu repository
$ make one CEU_SRC=/tmp/tst.ceu # compile a program
$ /tmp/tst                      # execute it
\end{verbatim}

As an example, the file \code{/tmp/tst.ceu} may contain a program such as
follows:

\begin{verbatim}
input int A; // two input events
input int B;

spawn do     // generates test inputs asynchronously
    await async do
        emit A(10);
        emit B(100);
    end
end

var int a = await A; // main program
var int b = await B;

escape a+b;  // 110 is the result of the program back to the OS
\end{verbatim}
